### 2018-04-11 paper/background.tex
changes to background

\subsubsection{Structure}
% definition of CHC
As stated in \autoref{sec:intro} a Constrained Horn Clause is a
logical implication where the antecedent is called the body and the
consequent is called the head.
%
The body is a conjunction of a logical formula, called the fact,
and a vector of uninterpreted predicates. The fact is an arbitrary
formula in some background logic, such as linear integer arithmetic.
%
The uninterpreted predicates are applied to variables which may or may
not appear in the fact.
%
A head can be either an uninterpreted predicate applied to variables or \cc{False}.
%
A Clause where the head is \cc{False} is called query.
\begin{defn}
  CHCs can be defined structurally:
\begin{align*}
  \cc{chc} &\Coloneqq \cc{head} \gets \cc{body} \\
  \cc{head} &\Coloneqq \cc{False} \\&\mid \cc{pred}  \\
  \cc{body} &\Coloneqq \varphi \wedge \cc{preds} \\
  \cc{preds} &\Coloneqq \cc{True} \\&\mid \cc{pred} \wedge \cc{preds} \\
  \cc{pred} &\Coloneqq \textsf{an uninterpreted predicate applied to variables} \\
  \varphi &\Coloneqq \textsf{a formula that all variables are vocabulary} \\
\end{align*}
\end{defn}
%
% define a body function, head function, and recursion-free
For a given CHC $C$, $\bodyof{C}$ denotes the vector of uninterpreted
predicates in the body of $C$ and $\consof{C}$ denotes the fact in the
body.
%
It is possible for an uninterpreted predicate to apper multiple times
in the body of $C$.
%
If $C$ is not a query, then $\headof{C}$ denotes the uninterpreted
predicate in the head.
%

%define a CHC system
A CHC system is a set of CHCs where exactly one clause is a query
%
For a given CHC system $S$, $\predof{S}$ denotes the set of all
uninterpreted predicates.

% define dependency predicates
\begin{defn}
  Given a CHC system $\cc{S}$ and two uninterpreted predicates $\cc{P}$ and
  $\cc{Q} \in \predof{S}$, if $\exists \cc{C} \in \cc{S}$ such that $\cc{P} = \headof{C}$
  and $\cc{Q} \in \bodyof{C}$, then $\cc{Q}$ is a dependency predicate of $\cc{P}$.
\end{defn}
%
\begin{ex}
  Because uninterpreted predicates \cc{L4} is in the body of clause (4) and uninterpreted predicates \cc{L8}
  is the head of clause (4), \cc{L4} is a dependency predicate of \cc{L8}.\autoref{chc}
\end{ex}
%
Given a CHC system $\cc{S}$ and an uninterpreted predicate $\cc{P}$, $\depsof{P}$
denotes the set of all dependency predicates of $\cc{P}$ in $\cc{S}$.
%

%define transitive dependency predicates
\begin{defn}
  Given a CHC system $\cc{S}$ and three uninterpreted predicates $\cc{P},
  \cc{Q}$ and $\cc{R} \in \predof{S}$, if $\cc{Q} \in \depsof{P}$ then \cc{Q} is a transitive dependency
  predicate of \cc{P}. 
  %
  if \cc{Q} is a transitive dependency predicate of \cc{P}, and \cc{R} is a transitive dependency predicate
  of \cc{Q},then $\cc{R}$ is a transitive dependency predicate of $\cc{P}$.
\end{defn}
%
\begin{ex}
  Because uninterpreted predicates \cc{L4} is a dependency predicate of \cc{L8}, 
  \cc{L4} is a transitive dependency predicate of \cc{L8}.
  %
  And because \cc{L8} is an transitive dependency predicate of \cc{L9}, 
  \cc{L4} is a transitive dependency predicate of \cc{L9}.\autoref{chc}
\end{ex}
%
Given a CHC system $\cc{S}$ and an uninterpreted predicate $\cc{P}$, $\tdepsof{P}$
denotes the set of all transitive dependency predicates of $\cc{P}$ in $\cc{S}$.
%

%define siblings
\begin{defn}
  Given a CHC system $\cc{S}$ and two uninterpreted predicates $\cc{P}$ and
  $\cc{Q} \in \predof{S}$, if $\exists \cc{C} \in \cc{S}$ such that $\cc{P} \in \bodyof{C}$
  and $\cc{Q} \in \bodyof{C}$, then $\cc{Q}$ and $\cc{P}$ are siblings of each other.
\end{defn}
%
\begin{ex}
  Because uninterpreted predicates \cc{L9} and \cc{db} both shows in the body of
  clause (6), \cc{L9} and \cc{db} are siblings of each other.
  %
\end{ex}
%
Given a CHC system $\cc{S}$ and an uninterpreted predicate $\cc{P}$, $\siblingof{P}$
denotes the set of all siblings predicates of $\cc{P}$ in $\cc{S}$.
%

%
For a given CHC system $\cc{S}$, there is no uninterpreted predicates $\cc{P} \in \predof{S}$ 
such that $\cc{P} \in \tdepsof{P}$, then $\cc{S}$ is a \emph{recursion-free} CHCs system.
%

%
A solution to a CHC system $S$ is a map that maps each each
uninterpreted predicate $\cc{P} \in \predof{S}$ to its interpretation which is a formula.
%
All clauses in $S$ holds
after substitute all uninterpreted predicates by its interpretation.

>>>>

\subsubsection{Structure}
% definition of CHC
As stated in \autoref{sec:intro} a Constrained Horn Clause is a
logical implication where the antecedent is called the body and the
consequent is called the head.
%
The body is a conjunction of a logical formula, called the fact,
and a vector of uninterpreted predicates. The fact is an arbitrary
formula in some background logic, such as linear integer arithmetic.
%
The uninterpreted predicates are applied to variables which may or may
not appear in the fact.
%
A head can be either an uninterpreted predicate applied to variables or \cc{False}.
%
A Clause where the head is \cc{False} is called query.
\begin{defn}
  CHCs can be defined structurally:
\begin{align*}
  \cc{chc} &\Coloneqq \cc{head} \gets \cc{body} \\
  \cc{head} &\Coloneqq \cc{False} \\&\mid \cc{pred}  \\
  \cc{body} &\Coloneqq \varphi \wedge \cc{preds} \\
  \cc{preds} &\Coloneqq \cc{True} \\&\mid \cc{pred} \wedge \cc{preds} \\
  \cc{pred} &\Coloneqq \textsf{an uninterpreted predicate applied to variables} \\
  \varphi &\Coloneqq \textsf{a formula that all variables are vocabulary} \\
\end{align*}
\end{defn}
%
% define a body function, head function, and recursion-free
For a given CHC $C$, $\bodyof{C}$ denotes the vector of uninterpreted
predicates in the body and $\consof{C}$ denotes the fact in the
body.
%
It is possible for an uninterpreted predicate to appear multiple times
in the body of $C$.
%
If $C$ is not a query, then $\headof{C}$ denotes the uninterpreted
predicate in the head.
%

%define a CHC system
A CHC system is a set of CHCs where exactly one clause is a query.
%
For a given CHC system $S$, $\predof{S}$ denotes the set of all
uninterpreted predicates.

% define dependency predicates
\begin{defn}
  Given a CHC system $\cc{S}$ and two uninterpreted predicates
  $\cc{P}$ and $\cc{Q} \in \predof{S}$, if $\exists \cc{C} \in \cc{S}$
  such that $\cc{P} = \headof{C}$ and $\cc{Q} \in \bodyof{C}$, then
  $\cc{Q}$ is a predicate dependency of $\cc{P}$.
\end{defn}
%
\begin{ex}
  In $\mcchc$, because $\cc{L}_4$ is in the body of clause (4) and
  $\cc{L}_8$ is the head of clause (4), $\cc{L}_4$ is a predicate
  dependency of $\cc{L}_8$.
\end{ex}
%
Given a CHC system $\cc{S}$ and an uninterpreted predicate $\cc{P}$,
$\depsof{P}$ denotes the set of all predicate dependencies of $\cc{P}$
in $\cc{S}$.
%

%define transitive dependency predicates
\begin{defn}
  Given a CHC system $\cc{S}$ and three uninterpreted predicates
  $\cc{P}, \cc{Q}$ and $\cc{R} \in \predof{S}$, if $\cc{Q} \in
  \depsof{P}$ then \cc{Q} is a transitive predicate dependency of
  \cc{P}.
  %
  If \cc{Q} is a transitive predicate dependency of \cc{P} and \cc{R}
  is a transitive predicate dependency of \cc{Q}, then $\cc{R}$ is a
  transitive predicate dependency of $\cc{P}$.
\end{defn}
%
\begin{ex}
  In $\mcchc$, because $\cc{L}_4$ is a predicate dependency of
  $\cc{L}_8$, $\cc{L}_4$ is a transitive predicate dependency of
  $\cc{L}_8$.
  %
  And because $\cc{L}_8$ is an transitive predicate dependency of
  $\cc{L}_9$, $\cc{L}_4$ is a transitive predicate dependency of
  $\cc{L}_9$.
\end{ex}
%
Given a CHC system $\cc{S}$ and an uninterpreted predicate $\cc{P}$,
$\tdepsof{P}$ denotes the set of all transitive predicate dependencies
of $\cc{P}$ in $\cc{S}$.
%

%define siblings
\begin{defn}
  Given a CHC system $\cc{S}$ and two uninterpreted predicates
  $\cc{P}$ and $\cc{Q} \in \predof{S}$, if $\exists \cc{C} \in \cc{S}$
  such that $\cc{P} \in \bodyof{C}$ and $\cc{Q} \in \bodyof{C}$, then
  $\cc{Q}$ and $\cc{P}$ are siblings.
\end{defn}
%
\begin{ex}
  Because uninterpreted predicates $\cc{L}_9$ and $\cc{db}$ both
  appear in the body of clause (6), $\cc{L}_9$ and $\cc{db}$ are
  siblings.
  %
\end{ex}
%
Given a CHC system $\cc{S}$ and an uninterpreted predicate $\cc{P}$,
$\siblingof{P}$ denotes the set of all predicate siblings of $\cc{P}$
in $\cc{S}$.
%
For a given CHC system $\cc{S}$, if there are no uninterpreted
predicate $\cc{P} \in \predof{S}$ such that $\cc{P} \in \tdepsof{P}$,
then $\cc{S}$ is a \emph{recursion-free} CHCs system.
%

A solution to a CHC system $S$ is a map from each uninterpreted
predicate $\cc{P} \in \predof{S}$ to its corresponding interpretation
which is a formula.
%
For a solution to be valid, each clause in $S$ must be valid after
substituting each uninterpreted predicate by its interpretation.
